\plaintitle

### 2016-05-27 cscw/papers/2017/labor/trackingWork.tex
comments that i should've pushed 6 hours ago yay for falling asleep

\subsection{Codify the common good}
\subsection{Decentralize the internet (again)}
\subsection{Deal with reputation}

\rule{\linewidth}{1pt}

>>>>

\subsection{Codify the common good}
As \citeauthor{lessig2006code} points out in his book,
digital media give designers the opportunity to design and build into the systems
policies and practices to contribute to the collective benefit of the people therein
\cite{lessig2006code}.
Historically, the confluence of forces \citeauthor{lessig2006code} describes
would ultimately result in outcomes such as benefits for workers,
funds for sick leave and vacation, and other conveniences.
The transient nature of on--demand work would seem to problematize this arrangement,
but we can discuss and explore the viability of building into systems the mechanisms necessary
to save a portion of payment from every gig,
record taxable income, or
myriad other generally administrative tasks automatically.

\subsection{Decentralize the internet (again)}
Digitally mediated on--demand labor markets have historically been insular and incompatible with one another,
forcing workers either to choose one or juggle participation in these markets with great difficulty.
Drivers

\subsection{Deal with reputation}

% \rule{\linewidth}{1pt}
